Detecting Facial Expressions in Professional Tennis Matches

### 2017-02-14 Report06-12.Rmd
glm modelling

####Analysis
The statistical analysis conducted to summarize and assess the validity of the method.
This method allowed all the software and the faces they found to be compared.

@@

```{r Regression, fig.cap = "\\label{Regression}"}
hitmiss <- function(x){
  allType <- c("Animetrics", "Google", "Microsoft", "Skybiometry")
  hit <- allType %in% x$type
  x[1,] %>%
    dplyr::select(file:visorhat) %>%
    cbind(type = allType, hit = hit)
}

glmFits <- ALLmetaIMGFaces %>%
  split(.$FaceKey) %>%
  map_df(~ hitmiss(.)) %>%
  split(.$type) %>%
  map(~ glm(hit ~ ., data = select(., -type, -file), family=binomial(link='logit')))

@@

## Significance of variables by software
#glmPlot %>%
#  mutate(significant = `Pr(>|t|)` < 0.05) %>%
#  filter(significant==TRUE) %>% 
#  droplevels(glmPlot$variable) %>% 
#  ggplot(aes(x=type, y=`Pr(>|t|)`)) + 
#  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
#  geom_col(aes(fill=significant))

glmx <- glmPlot %>%
  mutate(significant = `Pr(>|z|)` < 0.05) %>%
  filter(significant==TRUE) %>% 
  droplevels(glmPlot$variable) %>% 
  ggplot(aes(x=variable, y=`Pr(>|z|)`)) + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  geom_col(aes(fill=type)) 
glmx

@@

Regression analysis showed

@@

```{r Face-Bounding-Box-Data, results='hide', fig.cap = "Face Bounding Boxes Per Software: The bar chart above shows the number of Bounding Boxes produced by each software, comparing the height of the bars indicates that Google's Facial Recognition software recognized almost 1000 more faces than the next best software, Microsoft.\\label{Face-Bounding-Box-Data}"}
ggplot(ALLmetaIMG, aes(x = type, fill=type)) + geom_bar(position="dodge") +xlab("Facial Recognition Softwares")+scale_x_discrete(limits=c("Manual","Google","Microsoft","Skybiometry","Animetrics")) +ylab("Number of Potential Faces") + guides(fill=FALSE)
```

@@

```{r Face-Bounding-Box-UpSet, fig.cap = "Face Bounding Boxes Per Software Combination. The Bar Chart shows the Face Bounding Boxes that were recognised by multiple software. The largest group with 809 faces is Face Bounding Boxes only found by Manual annotations. The following group was Boxes representing the same faces being recognized by both Manual annotations and the Google API.\\label{Face-Bounding-Box-Upset}"}
createUpSet(ALLmetaIMGFaces)
```

```{r I3, results=TRUE, fig.cap = "There is an unusual classification where just right of the center, the smaller box actually captures a fist, not a face.\\label{fig:I3}"}
imagesList3<-as.list("2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png") 
overlayGgplot(imagesList3, ALLmetaIMGFaces, matchBox = FALSE)
```

@@

```{r Glasses, fig.cap = "This table shows the amount of faces recognised by google wearing glasses. The strong disparity between the amount of faces with glasses to faces without them means that the occurrence of these attributes across the software must be considered proportionally.\\label{tab:Glasses}"}
GlassesGoogle <- ALLmetaIMGFaces %>% filter(type=="Google") %>%
filter(matchesManual==TRUE)
pander(table(GlassesGoogle$glasses))
```

```{r Glasses-Figure, fig.cap = "The figure above shows that Google outperforms the other software, with or without glasses. When there are no glasses worn Google finds over 60% of the manually annotated faces.\\label{fig:Glasses-Figure}"}
ggplotProportion(ALLmetaIMGPlayers, glasses)+xlab("Glasses on Face")
```

@@

```{r Headangle-Figure, fig.cap = "Google performs much better in comparison to the other software when the head-angle is Profile. This is outperforming unusually well, however this could also be due to the poor performance of the software in this circumstance.\\label{fig:Headangle-Figure}"}
ggplotProportion(ALLmetaIMGPlayers, headangle)+xlab("Head Angle of Face")
```

>>>>

####Analysis

@@

Regression analysis showed that the situation attribute of an image was most influential in increasing the likelihood of a hit.
And head angle was most influential in decreasing.

```{r}
# Prepare data
library(purrr)
library(dplyr)
library(ggplot2)
hitmiss <- function(x){
  allType <- c("Animetrics", "Google", "Microsoft", "Skybiometry")
  hit <- allType %in% x$type
  x[1,] %>%
    dplyr::select(file:visorhat) %>%
    cbind(type = allType, hit = hit)
}

glmFits <- ALLmetaIMGFaces %>%
  split(.$FaceKey) %>%
  map_df(~ hitmiss(.)) %>%
  split(.$type) %>%
  map(~ glm(hit ~ . + visorhat*glasses, data = select(., -type, -file), binomial(link = "logit")))

@@

@@

```{r, Regression-Significance-Plot, fig.cap = "\\label{Regression--Significance-Plot}"}
## Significance of variables by software
glmPlot %>%
  mutate(significant = `Pr(>|z|)` < 0.05) %>%
  mutate(`Pr(<|z|)` = 1 - `Pr(>|z|)`) %>%
  ggplot(aes(x=type, y=`Pr(<|z|)`)) + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  geom_col(aes(fill=significant)) + 
  facet_wrap(~ variable)
```

The bar chart of the interaction of Glasses and Visors in \@ref(Regression--Significance-Plot) or Hats shows that when the face is accessorised with both, Google has a significantly increased chance of finding the face

```{r, Regression-Estimates-Plot, fig.cap = "\\label{Regression--Estimates-Plot}"}
## Significance of Estimated variable influences by software
glmPlot %>%
  mutate(significant = `Pr(>|z|)` < 0.05) %>%
  ggplot(aes(x=type, y=Estimate)) + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  geom_col(aes(fill=significant)) + 
  facet_wrap(~ variable, scales = "free_y")

#parallel coordinate plot, vars on x????
#unpack intercept
#don't force to zero
#convert into full model decription - every single level combination
#have every level and cross level - order combinations by p value
#function for estimates for each treatment
#multinomail 
```

```{r Regression-Situation-Table, fig.cap = "\\label{Regression-Situation-Table}"}

RegSituation<-glmPlot %>% subset(grepl("situation*", variable)) %>% select(variable, Estimate, type)

#RegSituation

data_wide <- spread(RegSituation, variable, Estimate)

names(data_wide)[names(data_wide)=="situationCourt player close-up"] <- "Court player close-up"
names(data_wide)[names(data_wide)=="situationCrowd"] <- "Crowd"
names(data_wide)[names(data_wide)=="situationOff court close up of player"] <- "Off court close up of player"
names(data_wide)[names(data_wide)=="situationCourt close-up not player"] <- "Court close-up not player"

kable(data_wide, format = "markdown", booktabs = TRUE, caption = "")
```

```{r Regression-Angle-Table, fig.cap = "\\label{Regression-Angle-Table}"}

RegHeadAngle<-glmPlot %>% subset(grepl("headangle*", variable)) %>% select(variable, Estimate, type)

#RegSituation

data_wideHead <- spread(RegHeadAngle, variable, Estimate)

names(data_wideHead)[names(data_wideHead)=="headangleOther"] <- "Other"
names(data_wideHead)[names(data_wideHead)=="headangleProfile"] <- "Profile"

kable(data_wideHead, format = "markdown", booktabs = TRUE, caption = "")
```

@@

```{r Face-Bounding-Box-Data, results='hide', fig.cap = "\\label{Face-Bounding-Box-Data} Face Bounding Boxes Per Software: The bar chart above shows the number of Bounding Boxes produced by each software, comparing the height of the bars indicates that Google's Facial Recognition software recognized almost 1000 more faces than the next best software, Microsoft."}
ggplot(ALLmetaIMG, aes(x = type, fill=type)) + geom_bar(position="dodge") +xlab("Facial Recognition Softwares")+scale_x_discrete(limits=c("Manual","Google","Microsoft","Skybiometry","Animetrics")) +ylab("Number of Potential Faces") + guides(fill=FALSE) + labs(caption="")
```

@@

```{r Face-Bounding-Box-UpSet, fig.cap = "\\label{Face-Bounding-Box-Upset} Face Bounding Boxes Per Software Combination. The Bar Chart shows the Face Bounding Boxes that were recognised by multiple software. The largest group with 809 faces is Face Bounding Boxes only found by Manual annotations. The following group was Boxes representing the same faces being recognized by both Manual annotations and the Google API."}
createUpSet(ALLmetaIMGFaces)
```

```{r I3, results=TRUE, fig.cap = "\\label{fig:I3} There is an unusual classification where just right of the center, the smaller box actually captures a fist, not a face."}
imagesList3<-as.list("2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png") 
overlayGgplot(imagesList3, ALLmetaIMGFaces, matchBox = FALSE)
```

@@

```{r Glasses, fig.cap = "\\label{tab:Glasses} This table shows the amount of faces recognised by google wearing glasses. The strong disparity between the amount of faces with glasses to faces without them means that the occurrence of these attributes across the software must be considered proportionally."}
GlassesGoogle <- ALLmetaIMGFaces %>% filter(type=="Google") %>%
filter(matchesManual==TRUE)
pander(table(GlassesGoogle$glasses))
```

```{r Glasses-Figure, fig.cap = "\\label{fig:Glasses-Figure} The figure above shows that Google outperforms the other software, with or without glasses. When there are no glasses worn Google finds over 60% of the manually annotated faces."}
ggplotProportion(ALLmetaIMGPlayers, glasses)+xlab("Glasses on Face")
```

@@

```{r Headangle-Figure, fig.cap = "\\label{fig:Headangle-Figure} Google performs much better in comparison to the other software when the head-angle is Profile. This is outperforming unusually well, however this could also be due to the poor performance of the software in this circumstance."}
ggplotProportion(ALLmetaIMGPlayers, headangle)+xlab("Head Angle of Face")
```
